Results Analysis

### 2024-11-02 analysis/Updated-ResultsAnalysis.Rmd
Updated results order
Ensured results reflects same order as manuscript

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  pdf_document: default
  html_document: default
---

@@

```{r}
# Load libraries
library(here)
library(lsr)
library(dplyr)
library(tidyverse)
library(tidylog)
library(binom)
library(ggplot2)
library(RColorBrewer)
library(assertthat)
library(kableExtra)
library(webshot2)
```

@@

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```
Run assertion checks for both samples
```{r}
# Check all randomly-selected and non-empirical journals have been removed from dj_prominent
assert_that(
  all(dj_prominent$sample_id == "prominent" | dj_prominent$sample_id == "both" 
      & dj_prominent$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

# Check all prominent sample and non-empirical journals have been removed from dj_random
assert_that(
  all(dj_random$sample_id == "random" | 
        dj_random$sample_id == "both" 
      & dj_random$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

## Journal characteristics
Descriptive statistics

prominentJIF
```

@@

@@

Count randomly selected journals listed as COPE members 
```{r}
randomCOPE <- dj_random %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

@@

RANDOMLY-SELECTED SAMPLE

@@

PROMINENT SAMPLE

@@

Find the most restrictive limits of any journal
```{r}
# Find the lowest length limit
minLength <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_name),
         ppc_length != "NOT STATED" & ppc_length != "Qualitative") %>%
 mutate(quantLength = as.numeric(ppc_length)) %>%
 slice_min(quantLength, n = 1) %>% # Select the row with the minimum quantLength
 ungroup()

@@

``` {r}
# Find the lowest time-to-submit limit
minTime <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_name),
         ppc_time != "NOT STATED" & ppc_time != "Qualitative") %>%
 mutate(quantTime = as.numeric(ppc_time)) %>%
 slice_min(quantTime, n = 1) %>% # Select the row with the minimum quantTime
 ungroup()

@@

Calculate CIs for linked PPC in articles in random sample
```{r}
# Linked PPCs
random_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  count()

@@

Calculate CIs for Linked PPC 
```{r}
sample_size_a <- 101

# Linked PPCs
prominent_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
         ppc_linked == TRUE) %>%
  count()

>>>>

---
title: "Results Analysis"
author: "Annie Whamond"
date: "2024-04-10"
output:
  html_document: default
  pdf_document: default
---

@@

```{r}
# Load libraries
library(here)
library(lsr)
library(dplyr)
library(tidyverse)
library(tidylog)
library(binom)
library(assertthat)
library(kableExtra)
library(webshot2)
```

@@

dj_random <- d_journals %>%
  filter(sample_id != "prominent") %>%
  filter(is_empirical == TRUE)
```

Run assertion checks for both samples
```{r}
# Check all randomly-selected and non-empirical journals have been removed from dj_prominent
assert_that(
  all(dj_prominent$sample_id == "prominent" | dj_prominent$sample_id == "both" 
      & dj_prominent$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )

# Check all prominent sample and non-empirical journals have been removed from dj_random
assert_that(
  all(dj_random$sample_id == "random" | 
        dj_random$sample_id == "both" 
      & dj_random$is_empirical == TRUE),
  msg = "Found unexpected values in the sample_id or is_empirical columns"
  )
```

## Journal characteristics

*Descriptive statistics*

@@

prominentJIF
```
Count randomly selected journals listed as COPE members 
```{r}
randomCOPE <- dj_random %>%
  filter(ppc_type == 'A') %>%
  filter(cope == TRUE) %>%
  summarise(count = n())

@@

*Supplementary Information I: Descriptive statistics for both journal samples*

@@

**RANDOMLY-SELECTED SAMPLE**

@@

**PROMINENT SAMPLE**

@@

Find the most restrictive length limit of any journal
```{r}
# Find the lowest length limit
minLength <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_length)) %>%
 filter(!is.na(ppc_name),
         ppc_length != "NOT STATED" & ppc_length != "Qualitative") %>%
 mutate(quantLength = as.numeric(ppc_length)) %>%
 slice_min(quantLength, n = 1) %>% # Select the row with the minimum quantLength
 ungroup()

@@

Find the most restrictive time limit of any journal
``` {r}
# Find the lowest time-to-submit limit
minTime <- d_journals %>%
 select(c(sample_id, journal_name, ppc_name, ppc_time)) %>%
 filter(!is.na(ppc_name),
         ppc_time != "NOT STATED" & ppc_time != "Qualitative") %>%
 mutate(quantTime = as.numeric(ppc_time)) %>%
 slice_min(quantTime, n = 1) %>% # Select the row with the minimum quantTime
 ungroup()

@@

Calculate CIs for linked PPC in articles in random sample
```{r}
# Specify sample size for articles (same for both samples)
sample_size_a <- 101

# Linked PPCs
random_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "random",
         ppc_linked == TRUE) %>%
  count()

@@

Calculate CIs for Linked PPC 
```{r}
# Linked PPCs
prominent_linked <- d_articles %>% # counts number of linked PPC events
  filter(sample_id == "prominent",
         ppc_linked == TRUE) %>%
  count()
